Engineering the Servo Web Browser Engine using Rust

### 2015-10-24 icse16-servo/servo.tex
Add conclusion. Fix typos.
Add jdm feedback. Fix urls in footnotes.

One area for future improvement is related to allocations that are not owned by Rust itself.
Today, we simply wrap raw C pointers in \lstinline[language=Rust]{unsafe} blocks when we need to use a
custom memory allocator or interoperate with the SpiderMonkey JavaScript engine from Gecko.
We have implemented wrapper types and compiler plugins that restrict incorrect uses of these foreign values,
but they are still a source of bugs and one of our largest areas of unsafe code.\footnote{https://blog.mozilla.org/research/2014/08/26/javascript-servos-only-garbage-collector/}

@@

In the future, we hope to expose our Rust libraries written for Servo to C, in order to reuse them
in the Firefox web brower.
A first potential library is our Rust-based URL parser.\footnote{https://github.com/servo/rust-url}
While URL parsing seems like a simple and secure task, an audit of the public security bugs\footnote{Firefox public security bugs: http://mzl.la/1GkOiIC} shows that all four of the ones that come from URL parsing are related to either indexing out of
range of a raw memory buffer or using data that had already been freed --- both of which are
prevented by Rust code.

>>>>

Rust also requires that all memory is initialized.
Failure to initialize memory also has led to crashes in Firefox.\footnote{\url{https://bugzilla.mozilla.org/show_bug.cgi?id=1088731}}

One area for future improvement is related to allocations that are not owned by Rust itself.
Today, we simply wrap raw C pointers in \lstinline[language=Rust]{unsafe} blocks when we need to use a
custom memory allocator or interoperate with the SpiderMonkey JavaScript engine from Gecko.
We have implemented wrapper types and compiler plugins that restrict incorrect uses of these foreign values,
but they are still a source of bugs and one of our largest areas of unsafe code.\footnote{\url{https://blog.mozilla.org/research/2014/08/26/javascript-servos-only-garbage-collector/}}

@@

In the future, we hope to expose our Rust libraries written for Servo to C, in order to reuse them
in the Firefox web browser.
A first potential library is our Rust-based URL parser.\footnote{\url{https://github.com/servo/rust-url}}
While URL parsing seems like a simple and secure task, an audit of the public security bugs\footnote{Firefox public security bugs: \url{http://mzl.la/1GkOiIC}} shows that all four of the ones that come from URL parsing are related to either indexing out of
range of a raw memory buffer or using data that had already been freed --- both of which are
prevented by Rust code.
